% !TEX root =  master.tex
\chapter{Quellenarbeit}

\section{Verwilt / prePrint / Vier Versionen}
https://www.medrxiv.org/content/10.1101/2020.07.17.20152702v4


\section{Calabrese / prePrint / Zwei Versionen}
https://www.medrxiv.org/content/10.1101/2020.12.21.20248431v2


\section{Viehweger / prePrint / Zwei Versionen}
https://www.medrxiv.org/content/10.1101/2020.04.16.20067603v2

Primärquellen in Zeile 24

Prevalence = Inzidenz / Anteil Infizierter in Population

Developed "Clonepool" - a software to calculate the Pool layouts under a BSD license https://github.com/phiweger/clonepool


11 when a traditional pool is tested positive, all samples in the pool need individual retesting, which becomes
12 ineffective at a higher proportion of positive samples.

14 At 2 Percent prevalence and 20 samples
15 per pool, our protocol increases screening capacity by factors of 5 and 2 compared to individual testing
16 and traditional pooling, respectively.

21 In most
22 laboratories, the screening capacity is limited by the number of PCR reactions that can be performed in
23 a day. It is, therefore, desirable to maximize the number of samples that can be tested per reaction.

27 A high prevalence renders traditional pooling ineffective.

50 We tested the proposed clonepool algorithm using simulated data. We assumed no pipetting errors,
51 which can be achieved, e.g., through the use of a pipetting robot. We also assume that 94 pools are
52 available, which corresponds to a 96-well plate with two wells reserved for a positive and a negative
53 control. Furthermore, we assume that there are no false positive or false negative PCR reactions.

61 The number of samples that can be pooled without affecting the PCR sensitivity is limited by the PCR
62 cycle threshold (Ct) for the target, i.e., the cycle at which amplification becomes detectable over back
63 ground noise (typically ten times the standard deviation, SD). Usually, Ct values above 35 are treated
64 as unspecific amplification. SARS-CoV-2 amplifies at low Ct values due to high viral titers (Ct 18-25
65 depending on the material and number of days post-infection).4,5 A 20-fold dilution, i.e., pooling 20 sam-
66 ples, would cause the Ct value to increase by about 4.3 cycles (2𝑥 = 𝑑, where d is the dilution and x the
67 shift in Ct), which still lies comfortably above the detection limit.